### 2022-07-03 latex/Chapters/SlidingPuzzle.tex
update

\subsection{Solving the hardest problem}
To finish with the 3x3 SP, let me try to throw one of the two hardest 3x3 configurations (see subsection \ref{sec:SPLowDimension}) at the different solvers to see how they fare. The results are shown here

@@

blabla

@@

blabla

>>>>

\subsection{Solving the hardest 3x3 problem}
To finish with the 3x3 SP, let me try to throw one of the two hardest 3x3 configurations (see subsection \ref{sec:SPLowDimension}) at the different solvers to see how they fare. The results are shown here

@@

TBD

@@

TBD

%-----------------------------------
%	SECTION 5
%-----------------------------------

\section{5x5}

TBD
